### 2025-01-19 paper/icml25/first/sects/shacpp.tex
prefer Cref on ref
typo on shacpp

Similarly, we aim to train a neural network to approximate the transition function. However, to avoid vanishing or exploding gradients, we employ a non-recursive approach similar similar to Action World Model~\cite{Ma24}. This corresponds to train a neural network that given a starting observation from $\mathcal{S}$ and a sequence of $H$ actions from $\mathcal{A}^H$, predicts the next $H$ observations from $\mathcal{S}^H$. We aim to minimize:

@@

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. A minimal pseudocode of our algorithm is presented in \ref{alg:shacpp}. Figure~\ref{fig:shacpp} presents an unrolled view of the \fname{} algorithm.

>>>>

Similarly, we aim to train a neural network to approximate the transition function. However, to avoid vanishing or exploding gradients, we employ a non-recursive approach similar to Action World Model~\cite{Ma24}. This corresponds to train a neural network that given a starting observation from $\mathcal{S}$ and a sequence of $H$ actions from $\mathcal{A}^H$, predicts the next $H$ observations from $\mathcal{S}^H$. We aim to minimize:

@@

To summarize, our algorithm, aims to minimize the 4 presented losses, $\mathcal{L'}_\theta^{\pi}$, $\mathcal{L}_\theta^V$, $\mathcal{L}_\theta^R$, and $\mathcal{L}_\theta^F$. A minimal pseudocode of our algorithm is presented in \Cref{alg:shacpp}. \Cref{fig:shacpp} presents an unrolled view of the \fname{} algorithm.
